Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-01 paper/main.tex
Working on GPU implementation section

Based on the strength of the results for our single-kernel implementation, we chose to follow
a single kernel strategy for the alignment stage.

% DREW Idea... in hindsight, maybe we should still try many kernel launches, even if it
% means individual instances can't terminate early.

@@

>>>>

Our proposed GPU implementation for the iterative alignment stage consists of a
single kernel that performs all of the test image alignment problems.  Each of
instance of the alignment problem is assigned its own thread block, and the GPU
hardware schedules as many of these thread blocks to run concurrently as the 
hardware will allow.

% DREW Idea... in hindsight, maybe we should still try many kernel launches. 
% instances can still exit early, and can still update a global variable signaling
% that they're done

%even if it
% means individual instances can't terminate early.

@@

\begin{figure}[sim_plot]
\begin{center}
      \includegraphics{../results/random_data/time_vs_matrix_size_constant_tol.svg}
\end{center}
\caption{Speed vs Dimensions of A.  Outer loop tolerance = 0.1.  Inner loop tolerance = $10^{-5}$}
\end{figure}
